### 2016-08-24 rebuttal.tex

\question The footnote 4 should be moved from line 221 to line 222, right after ``Basic''.
\label{rev3point16}
\begin{solution}
We have made the suggested change.
\end{solution}

\question The part ``which defines some basic methods for symbolic expression trees'' should be removed from line 222, as it was already given in line 130.
\begin{solution}
This part was removed and footnote moved to the mentioned
text in the section 2.2, ``The Core''.
\end{solution}

\question In line 225, the sentence ``Not all SymPy classes are subclasses of \texttt{Expr}.'' sounds confusing as a reader new to SymPy wouldn't expect, for example, symbols to inherit ``Expr''. It would be better to expand this, for example ``Most of the SymPy classes (including \texttt{Symbol}) are subclasses of \texttt{Expr}, but there are exceptions to this rule''.
\begin{solution}
This paragraph now reads:
\begin{quote}
The typical way to create a custom SymPy object is to subclass an existing
SymPy class, usually \texttt{Basic}, \texttt{Expr}, or \texttt{Function}. As
it was stated before, all SymPy classes used for expression trees should be
subclasses of the base class \texttt{Basic}. \texttt{Expr} is the
\texttt{Basic} subclass for mathematical that can be added and multiplied
together. The most commonly seen classes in SymPy are subclasses of
\texttt{Expr}, including \texttt{Add}, \texttt{Mul}, and \texttt{Symbol}.
Instances of \texttt{Expr} typically represent complex numbers, but may also
include other ``rings'', like matrix expressions. Not all SymPy classes are
subclasses of \texttt{Expr}. For instance, logic expressions, such as
\verb|And(x, y)|, are subclasses of \texttt{Basic} but not of \texttt{Expr}.
\end{quote}
\end{solution}

\question The title ``Features'' in line 276 is ambiguous, as a ``feature''
has no precise meaning in Python (or even software libraries in general). It
should be replaced by ``Packages and modules'' or a similar more precise
wording. The same goes for ``feature'' in most other places in the paper (for
example, the caption of Table 1.\ and line 495). It would be very useful to also include actual names of the packages/modules in Table 1., as well as in any section covering those packages/modules.
\begin{solution}
IEEE 829 defines the term feature as ``a distinguishing
characteristic of a software item (e.g., performance, portability,
or functionality).''  We believe, that this definition fits our needs.

### 2016-08-26 rebuttal.tex

Emphasize that the environment variable \texttt{SYMPY\_DEBUG} must be set before importing SymPy for the first time.
\begin{solution}
Footnote was added right before the final example from the Gruntz algorithm section.
\end{solution}

\question In line 183, syntax \texttt{symbols(\textquotesingle{}a:d\textquotesingle{})} is used without being previously defined or explained.
\begin{solution}
Now we use \texttt{symbols(\textquotesingle{}a b c d\textquotesingle{})}, like in other places.
\end{solution}

\question Figure 2 should not be a screenshot, but rather proper code with \LaTeX-rendered results and explanations, as was done in the rest of the paper. A
 shortened link to SymPy Gamma for the example's expression can be included
 for the user to try this for themselves.
\begin{solution}
We believe this is not a good idea.  This figure is meant to be an archival
capture, not software subject to being re-rendered. SymPy Gamma currently only
renders as HTML\@. SymPy Gamma doesn't export output as \LaTeX{} or other external
formats.

A URL to the project site was added.
\end{solution}

### 2016-08-26 architecture.tex
Make it clear that SymPy 1.0 doesn't use SymEngine
sympy.mechanics -> sympy.physics.mechanics
Fix some minor LaTeX issues

The \texttt{Function} class is a subclass of \texttt{Expr} which makes it
easier to define mathematical functions called with arguments. This includes
named functions like $\sin(x)$ and $\log(x)$ as well as undefined functions
like $f(x)$. Subclasses of \texttt{Function} should define a
class method \texttt{eval}, which returns a canonical form of the function
application (usually an instance of some other class, i.e. a \texttt{Number})
or \texttt{None}, if for given arguments that function should not be
automatically evaluated.

@@

For this reason, a new library called SymEngine~\cite{SymEngine} was started.
It is a pure C++ library with thin wrappers to other languages (Python, Ruby,
Julia, ...) whose aim is to be the fastest manipulation library.  Preliminary
benchmarks suggest that SymEngine is as fast or faster than the commercial or
open source competitors.

SymPy recently started to use SymEngine as an optional backend, initially in
\texttt{sympy.mechanics} only. The plan is to allow more algorithms in SymPy to
take advantage of the speed of SymEngine.

>>>>

The \texttt{Function} class is a subclass of \texttt{Expr} which makes it
easier to define mathematical functions called with arguments. This includes
named functions like $\sin(x)$ and $\log(x)$ as well as undefined functions
like $f(x)$. Subclasses of \texttt{Function} should define a
class method \texttt{eval}, which returns a canonical form of the function
application (usually an instance of some other class, i.e., a \texttt{Number})
or \texttt{None}, if for given arguments that function should not be
automatically evaluated.

@@

For this reason, a new library called SymEngine~\cite{SymEngine} was started.
It is a pure C++ library with thin wrappers to other languages (Python, Ruby,
Julia, \ldots) whose aim is to be the fastest manipulation library.  Preliminary
benchmarks suggest that SymEngine is as fast or faster than the commercial or
open source competitors.

The development branch of SymPy recently started to use SymEngine as an
optional backend, initially in \texttt{sympy.physics.mechanics} only. The plan is
to allow more algorithms in SymPy to take advantage of the speed of SymEngine.
